Wrangle 18s rel abund data

### 2019-10-30 code/wrangle/wrangle_18s_rel_abund.Rmd
write out 18s asv_id - seq key file

write clean csv as output
```{r}
clean_18s_ra_path <- here("data/clean/clean_18s_ra.csv")
write_csv(clean_18s_ra, clean_18s_ra_path)
```

>>>>

write clean csv as output
```{r}
clean_18s_ra_path <- here("data/clean/clean_18s_ra.csv")
write_csv(clean_18s_ra, clean_18s_ra_path)

asv_path <- here("intermediate_output/asv_seq_key_18s.csv")
write_csv(asv_seq_key_18s, asv_path)
```
